Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-06 trunk/SAiP/Module1/H1/doc/paper.tex
Update of the IEEE Conformance section and other smaller changes.

@@

\date{2008-02-04 13:32}

@@

% ---------------------------------------------------------------------
\subsection{Module Viewpoint}

The module viewpoint of the HS07 system.

@@

% ---------------------------------------------------------------------
\subsection{Component \& Connector Viewpoint}
\label{sec:component}

@@

% ---------------------------------------------------------------------
\subsection{Allocation Viewpoint}

The allocation viewpoint illustrates how components are deployed in actual
processes within the HS07 system.

@@

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{itemize}
\item \emph{Stakeholders and their concerns}. This encompasses both users/aquirers and developers.
\item \emph{Feasibility}
\item \emph{Maintainablity}
\item \emph{Security} How is the Gateway protected? What protection is there against attack and inproper use? 
\item \emph {Safety} How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item \emph{Availability} What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item \emph{Testability} What is the tesability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{itemize}

@@

The following are the problems identified in order to comply with \cite{ieeerecommendedpractice}.

Clause 5.2: The stakeholders and their precise concerns need to be identified for each view.

Clause 5.5: Consistency checks across all existing views.

>>>>

\renewcommand{\descriptionlabel}[1]
    {\hspace{\labelsep}\emph{#1}}

@@

\date{2008-02-06}

@@

% ---------------------------------------------------------------------
\subsection{Module View}

This section contains the module view of the HS07 system. This view
is based on the Module Viewpoint as defined in \cite{christensen2004archdesc}.

@@

% ---------------------------------------------------------------------
\subsection{Component \& Connector View}
\label{sec:component}

This section contains the Component \& Connecter view of the HS07 system.
This view is based on the Component \& Connecter viewpoint as defined in
\cite{christensen2004archdesc}.

@@

% ---------------------------------------------------------------------
\subsection{Allocation View}

This section contains the allocation view of the HS07 system. This view
is based on the Allocation Viewpoint as defined in \cite{christensen2004archdesc}.

The allocation view illustrates how components are deployed in actual
processes within the HS07 system.

@@

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{description}
\item[Stakeholders and their concerns] This encompasses both users/aquirers and developers.
\item[Feasibility]
\item[Maintainablity]
\item[Security] How is the Gateway protected? What protection is there against attack and inproper use? 
\item[Safety] How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item[Availability] What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item[Testability] What is the testability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{description}

@@

This section describes how this architectural description conforms to recommended practice
that is defined in \cite{ieeerecommendedpractice}.

\begin{description}
	\item[Clause 5.1 Architectural documentation] This report does not include a change history
		and a glossary as defined in the recommended practice. (XXX: scope, context?)
	\item[Clause 5.2 Identification of stakeholders and concers] The stakeholders of this system and
		their precise concerns have not been identified in this report. This must be done in order to
		conform to the recommended practice.
	\item[Clause 5.3 Selection of architectural viewpoints] The viewpoints used in this architectural
		description are defined in \cite{christensen2004archdesc}.
	\item[Clause 5.4 Architectural views] This report contains the following architectural views: Module
		View, Component \& Connector View and Allocation View.
	\item[Clause 5.5 Consistency among architectural views] There is no consistency check across the views
		in this report as specified in the recommended practice.
	\item[Clause 5.6 Architectural rationale] There is no rationale for the architectural decisions
		that have made in this report.
\end{description}
